### 2013-03-06 doc/final_report/implementation.tex

The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
\url{http://www.arxiv.org/} were suggested as sources for more open access
articles that could be added to Partridge. Both of these sites were found to
contain large volumes of open access papers. However, most of these papers were
published as PDF files which meant that some conversion would be required to
make them compatible with Partridge.

>>>>

The `mega-journals' PLOSOne \url{http://www.plosone.org/} and arXiv
\url{http://www.arxiv.org/} were suggested as sources for more open access
articles that could be added to Partridge. Both of these sites were found to
contain large volumes of open access papers. Most of the journals stored on the
arXiv site were in PDF format which, as discussed below, are difficult to
convert and annotate. However, PLOSOne use the SciXML markup language for
papers published through their journal, which made converting and annotating
them a lot simpler for Patridge. PLOSOne also publish all of their papers under
the Creative Commons Share-Alike-By-Attribution license\cite{ccbyattr}. This
meant that as long as the author information was left intact, all of the papers
could be used for data mining purposes.

\subsubsection{Acquiring Scientific Papers}
Once PLOSOne was identified as a suitable source of papers, a method for
acquiring large batches of papers to be processed was formulated.

### 2013-03-06 doc/final_report/introduction.tex
Wrote abstract and got the main layout looking a bit nicer

%%%%------------------------------------------------
%
%  Include for chapter one of dissertation: introduction
%
%%%%------------------------------------------------
\subsection{Context}

@@

\subsection{Objectives}

@@

From the point of view of its users, Partridge will assist researchers in two
ways. The system will provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their result, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. Depending upon the time constraints of the
project, it is hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.

\subsection{Background}

\subsubsection{ Related Works }

@@

\subsection{ Literature Review}

\subsubsection{Natural Language Processing}

@@

\subsubsection{CISP, CoreSC and SAPIENTA}

>>>>

%%%%------------------------------------------------
%
%  Include for chapter one of dissertation: introduction
%
%%%%------------------------------------------------
\section{Context}

@@

\section{Objectives}

@@

From the point of view of its users, Partridge was designed to assist
researchers in three principal ways.

\begin{itemize}
\item The system should provide search within specific CoreSC regions of a given
paper. This would allow users to find the most relevant papers to them. For
example a user may search for "mass spectrometer" within the methodology
section of a paper.
\item The system should provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their result, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. 
\item Depending upon the time constraints of the
project, it is hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.

\end{itemize}

\section{Background}

\subsection{ Related Works }

@@

\section{ Literature Review}

\subsection{Natural Language Processing}

@@

\subsection{CISP, CoreSC and SAPIENTA}

### 2013-03-06 doc/final_report/report.tex

Finally, I am eternally grateful for the support of my family and friends who
have put up with my gripes and moans throughout the duration of this project
and without whom, I couldn't have achieved such an ambitious project.

>>>>

Finally, I am eternally grateful for the support of my family and friends who
have put up with my gripes and moans throughout the duration of this project
and without whom, I may have given up hope on my dissertation.
